\documentclass[a4paper]{article}
    \usepackage{fullpage}
    \usepackage{amsmath}
    \usepackage{amssymb}
    \usepackage{textcomp}
    \usepackage[utf8]{inputenc}
    \usepackage[T1]{fontenc}
    \usepackage{geometry}
    \geometry{textwidth=6.7in, top=1in, bottom=0in}
    \textheight=10in
    \pagestyle{empty}
    \raggedright
    
    \usepackage{lmodern}

    %\renewcommand{\encodingdefault}{cg}
%\renewcommand{\rmdefault}{lgrcmr}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

% DEFINITIONS FOR RESUME %%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\area} [2] {
    \vspace*{-9pt}
    \begin{verse}
        \textbf{#1}   #2
    \end{verse}
}

\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-18pt} \hrulefill \\
}

\newcommand{\header} [1] {
    {\hspace*{-18pt}\vspace*{6pt} \textsc{#1}}
    \vspace*{-6pt} \lineunder
}

\newcommand{\employer} [3] {
    { \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }
}

\newcommand{\contact} [3] {
    \vspace*{-10pt}
    \begin{center}
        {\Huge \scshape {#1}}\\
        #2 \\ #3
    \end{center}
    \vspace*{-8pt}
}

\newenvironment{achievements}{
    \begin{list}
        {$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}
    \end{list}
}

\newcommand{\schoolwithcourses} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
    \vspace*{5pt}
}

\newcommand{\school} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
}
% END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%

    \begin{document}
\vspace*{-40pt}

    

%==== Profile ====%
\vspace*{-10pt}
\begin{center}
	{\Huge \scshape {Loïc Murumba}}\\
	lmurumba@edu.uwaterloo.ca $\cdot$ 613-700-4103 $\cdot$ https://loic.ml\\
\end{center}

%==== Experience ====%
\header{Work Experience}
\vspace{1mm}

\textbf{Google} \hfill Waterloo, ON\\
\text{Intern} \hfill May 2018 | Aug 2018\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Developed and designed tab in existing review tool to streamline suspicious advertisement review process.
    	\item Reduced number of tools required to evaluate malicious advertisements by 75\% by consolidating information from multiple data sources into the new tab.
    \item Investigated suspicious ads and analyzed what signals are associated with unacceptable behaviour in different ad products. Designed the tab to highlight these signals.
	\item Implemented feature extractors for ad information in existing feature repository using C++.
	\item Deployed changes in multiple binaries hosted in different data centers; organized communication between these using remote procedure calls and learned distributed computing concepts.
	\item Made changes to review tab frontend with Python, JavaScript, Google Closure library, and CSS.

\end{itemize}

\textbf{Mitre Media} \hfill Toronto, ON\\
\text{Software Developer} \hfill Sept 2017 | Dec 2017\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Implemented automated stock reliability ranking using Rails and MySQL. Over 6000 stocks ranked daily using this algorithm.
	\item Converted outdated PHP account registration process to use Ruby on Rails backend and managed release process for the new changes.
	\item Tripled page views and improved user experience on dividend stock search tool by building helpful filters.
\end{itemize}

\header{Activities}
\vspace{1mm}

\textbf{StarterHacks} \hfill \\
\text{Organizer} \hfill Sept 2018 | Present\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
    \item Implementing signup page using Node.js and React to handle requests from thousands of users.
    \item Updating QR code scanner app that will be used with assigned badges to register and verify participants throughout the event.
    \item Outlined user model used for organizing applications and registrations in a mongoDB database.
\end{itemize}

\textbf{Midnight Sun Solar Race Car Team}\\
\text{Web Developer} \hfill May 2017 | Nov 2017\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Designed and implemented new website to represent the team using HTML, CSS, and Javascript.
	\item Regularly updated the website to include recent sponsorship updates.
	\item Website can be viewed at uwmidsun.com.
\end{itemize}

\header{Projects}
{\textbf{Stock History (in progress)}} {\ \textbar{} Python, pandas, PyQt } \\
Python app allowing users to find historical stock information using Quandl API.\\
Implementing backtesting of a moving average trading strategy on stocks that are displayed.\\
\vspace*{2mm}

{\textbf{Platformer AI}} {\ \textbar{} Javascript, HTML} \\
Machine learning demo of neural networks attempting to beat a simple platform game by dodging obstacles.\\
Designed genetic algorithm to improve performance over time.\\
\vspace*{2mm}

{\textbf{FoodFeed}} {\ \textbar{} Javascript, Java, Swift} \hfill https://foodfeed.ml\\
Mobile app allowing users to easily browse through and save GIF versions of recipe videos.\\
Developed script to populate database with GIFs and to categorize them for intuitive browsing. \\
\vspace*{2mm}

{\textbf{Soar}} {\ \textbar{} Java} \hfill http://soar-game.ml\\
Challenging android platformer where the player avoids incoming obstacles; 500+ installs in Google Playstore.\\
Implemented a database so that users can see and update the world wide high score.\\
\vspace*{2mm}

%==== Education ====%
\header{Education}
\textbf{University of Waterloo}\hfill Waterloo, ON\\
3A B.S Computer Science \textit{GPA: 3.8} \hfill Sept 2016 - Present\\
Co-op Student of the Year Candidate for outstanding work term performance evaluations


\vspace{2mm}

\ 
\end{document}
